---
title: "P8105 HW1"
author: "Wenbo Fei(wf2270)"
date: "9/19/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1
Create a data frame with the specified elements.
```{r create_df}
prob1_df1 = tibble(
  num1 = rnorm(10),
  logi1 = num1 > 0,
  char1 = c("one","two","three","four","five","six","eight","seven","nine","ten"), 
  fac1 = factor(sample(c("A","B","C"), 10, replace = TRUE))
)
```

Take the mean of each variable in my data frame.
```{r mean_pull_var}
mean(pull(prob1_df1, num1))
mean(pull(prob1_df1, logi1))
mean(pull(prob1_df1, char1))
mean(pull(prob1_df1, fac1))
```

I can take the mean of numbers and logical but not character or factor. 

```{r try_numeric, results='hide'}
as.numeric(pull(prob1_df1, num1))
as.numeric(pull(prob1_df1, logi1))
as.numeric(pull(prob1_df1, char1))
as.numeric(pull(prob1_df1, fac1))
```

We got NA when to apply as.numeric to charactor variables. Logical variables will be transformed into 0 or 1 so it can be taken the mean. Factor variables will be transformed into levels if \'level=T\' when we create the factor variables, but we can't do math calculation on factors.

Second code trunck
```{r numeric_multiply}
as.numeric(pull(prob1_df1, logi1)) * pull(prob1_df1, num1)
as.factor(pull(prob1_df1, logi1)) * pull(prob1_df1, num1)
as.numeric(as.factor(pull(prob1_df1, logi1))) * pull(prob1_df1, num1)
```

#Problem 2
```{r data_describ}
data("penguins", package = "palmerpenguins")
#the data in this dataset, including names / values of important variables
head(penguins)
summary(penguins)
#the size of the dataset 
nrow(penguins)
ncol(penguins)
#mean flipper length
mean(pull(penguins,flipper_length_mm), na.rm = T)
```

```{r plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```